\documentclass[letterpaper,11pt]{article}
\setcounter{secnumdepth}{0}

\usepackage{geometry}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{gfsdidot}
\usepackage{chngpage}
\usepackage{enumitem}

\color[HTML]{101010}
\setlist[itemize]{leftmargin=*}

\geometry{
  inner=0.5in,
  top=1.5cm,
  bottom=1.5cm,
  right=1.5cm,
  left=1.5cm
}

{\setlength{\parindent}{0cm}

\titleformat{\section}
  {\scshape\color[HTML]{050505}}{\thesection}{1em}{}[\titlerule]

\titlespacing*{\subsection}{0pt}{2ex}{0pt}

\begin{document}

\begin{flushleft}
\Large{\textbf{Jesse Kelly}}
\hfill
kellyjesse881@gmail.com
\newline
Full Stack Developer
\hfill
+1 614 398 0239
\end{flushleft}

\section{About Me\hfill http://jessekelly.tk/}
Full Stack Developer with four years of both
professional and academic experience in frontend
and backend programming. My primary areas of
expertise are \textbf{Django}, web development using \textbf{HTML5},
\textbf{CSS3}, and \textbf{JS}, \textbf{Typescript}, and app development using
\textbf{Angular}, \textbf{Ionic}, and \textbf{Progressive Web Apps(PWAs)}.

\section{Relevant Skills\hfill github.com/jessekelly881}
\begin{itemize}
\item \textbf{Django}: Experience building backends using Python and Django and implimenting complex \textbf{REST APIs} using tastipie.
\item \textbf{Angular}: Experience working with Angular alongside Ionic to develop cross platform(Android, iOS, and Web) apps. Deep understanding of Angular including experience defining models, components, guards, and interceptors, as well as interacting with REST API's.
\item \textbf{Docker}: Experience creating Dockerfile and docker-compose files in addition to using docker as a regular part of development.
\item \textbf{Git}: Experience using Git porcelain and plumming(e.g. cat-file, and hash-object) commands including merge and rebase as well as writing git hooks. Posesses a deep understanding of Git internals.
\end{itemize}

\section{Experience\hfill 5+ years}
\subsection{Appuntos}
\textit{Full Stack Developer}
\vspace{2mm}
\begin{adjustwidth}{1cm}{1cm}
Developed customized android and ios
app using Angular 6, Cordova, and Ionic.
Improved backend built using Django,
Postgres, Redis, and Material CSS. Used
Docker, Git, and Gitlab as a regular part
of development lifecycle.
\end{adjustwidth}

\subsection{Zima}
\textit{Co-Founder, CTO}
\vspace{2mm}
\begin{adjustwidth}{1cm}{1cm}
Designed and developed websites and web
apps for numerous applications using
HTML, CSS, JS, Bootstrap and Material CSS.
Also, ran DevOps using AWS, Terraform,
Git, and Netlify.
\end{adjustwidth}
\section{Education\hfill B.A. Mathematics}
\subsection{The Ohio State University}
\textit{B.A. Mathematics}
\vspace{2mm}
\begin{adjustwidth}{1cm}{1cm}
\textbf{Minors}: History, Logic(Philosophy)
\end{adjustwidth}
\section{Further Skills And Education\hfill Life Long Learner}
\textbf{Languages Spoken: } English(Native), Spanish(Fluent), French(Inter.)
\newline
\textbf{\LaTeX}: Used to build this resume. Source code available.
\newline
\textbf{Linux \& Emacs}: I use Arch Linux(with i3wm) and Emacs and writing bash and emacs lisp is my hobby.
\newline
\end{document}
