\documentclass[letterpaper,11pt]{article}
\setcounter{secnumdepth}{0}
\pagenumbering{gobble}
\definecolor{primary}{RGB}{0,0,51}
\color{red}

\usepackage{geometry}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{gfsdidot}
\usepackage{chngpage}
\usepackage{enumitem}
\usepackage{inconsolata}
\usepackage[hidelinks]{hyperref}

\color[HTML]{101010}
\setlist[itemize]{leftmargin=*}

\geometry{
  inner=0.5in,
  top=1.5cm,
  bottom=1.5cm,
  right=1.5cm,
  left=1.5cm
}

{\setlength{\parindent}{0cm}

\titleformat{\section}
  {\scshape\color[HTML]{050505}}{\thesection}{1em}{}[\titlerule]

\titlespacing*{\subsection}{0pt}{2ex}{0pt}

\begin{document}

\begin{flushleft}
\Large{\textbf{Jesse Kelly}}
\hfill
\texttt{kellyjesse881@gmail.com}
\newline
Full Stack Web Engineer
\hfill
\texttt{+1 614 398 0239}
\end{flushleft}

\section{About Me}
A humble engineer with a passion for languages, technology, and solving problems.
Has four years of experience taking projects from the whiteboard to the client.

\vspace{2mm}
Languages spoken: English(Native), Spanish(Fluent/C1), French(Inter./B1)

\vspace{2mm}
Currently living in Mexico City. Willing to travel.


\section{Relevant Skills}
\href{https://github.com/jessekelly881}{\texttt{github.com/jessekelly881}}
\begin{itemize}
\setlength\itemsep{0em}
\item Frontend: React, Redux, Angular, Ionic, Cordova, Capacitor, PWAs, SASS, Typescript, JS, CSS3, HTML5
\item Backend: Django, Celery, Flask, REST, Postgres, Redis, GraphQL, Hasura
\item DevOps: Docker, Git, AWS, Gitlab
\item Systems: Linux, Bash, Make, Awk
\item Misc: Emacs Lisp, \LaTeX
\end{itemize}

\section{Experience}
\subsection{\href{https://www.appuntos.com/}{Appuntos}}
\textit{Tech Lead, Full Stack Engineer}
\vspace{2mm}
\begin{adjustwidth}{1cm}{1cm}
  Startup based in Mexico City dedicated to improving customer loyalty

\begin{itemize}
\item Successfully lead a small team to develop new web application built using \textbf{React}, \textbf{Redux}, \textbf{MongoDB}, and \textbf{Express}.
\item Lead deployment of application to \textbf{Amazon Web Services(AWS)} using \textbf{Docker}.
\item Maintained legacy \textbf{Ionic} and \textbf{Cordova} application, as well as dashboard build in \textbf{Django} and \textbf{Angular} respectively.
\item Ensured that good coding hygine was maintained across the product development cycle.
\end{itemize}

\end{adjustwidth}

\subsection{\href{https://zima.xyz/}{Zima}}
\textit{Founder, Full Stack Engineer}
\vspace{2mm}
\begin{adjustwidth}{1cm}{1cm}
A website and app development company specializing in PWAs and Hybrid apps.

\begin{itemize}
\setlength\itemsep{0em}
\item Lead team of two other developers in building and deploying applications rapidly and reliably using \textbf{AWS} and \textbf{Docker}
\item Worked directly with clients to develop MVPs for their products and ensure that their specifications were translated to the other developers.
\item Developed cross platform web and mobile applications using \textbf{React}, \textbf{Redux}, \textbf{Ionic}, \textbf{Capacitor}, and \textbf{Typescript}
\item Built and maintained internal javascript library to aid in the rapid development of applications for clients
\end{itemize}

\end{adjustwidth}

\section{Education}
\subsection{\href{https://www.osu.edu/}{The Ohio State University}}
\textit{B.A. Mathematics(Theoretical Track)}
\vspace{2mm}
\begin{adjustwidth}{1cm}{1cm}
\textit{Mathematical Statistics I,II}: Learned advanced statistical methods including Confidence Intervals, Regression Analysis, and ANOVA Tests. Also, experience using R for data analysis.

\vspace{2mm}
\textit{Advanced Logical Theory}: An advanced cource covering the mathematical foundations of computation
including complete mathematical proofs of Godel's Incompleteness Theorems
\end{adjustwidth}
\end{document}
